---
title: Revolutions Blog [A data science investigation on the NYT anonymous op-ed]
author: Elleni Toumpas
date: '2018-09-10'
slug: revolutions-blog-a-data-science-investigation-on-the-nyt-anonymous-op-ed
categories:
  - R
tags:
  - project breakdowns
Categories:
  - Development
  - GoLang
Description: ''
Tags:
  - Development
  - golang
menu: main
---

Starting a new data anaylsis project at the moment feels so overwhelming. There are so may techniques I currently don't understand OR am even aware of. To overcome this I have decided to research other data scientists/ analysts and the steps they take in their own project By understanding their projects, the tools and algorithms they have used and understanding why they might have chosen those techniques I hope to become more proficient and confident in this industry. I am going to call these blog write ups Project Breakdowns.

My first Project Breakdown is inspired by the ["Who wrote that anonymous NYT op-ed? Text similarity analyses with R"](http://blog.revolutionanalytics.com/2018/09/anonymous-nyt-op-ed.html) blog article on the [Revolution Analytics](http://blog.revolutionanalytics.com/) website. The article introduces the New York Times anonymous op-ed written by a current White House staffer who reports that many staffers inside the White House are working silently to oppose or thwart Donald Trump's agenda. The [Revolution Analytics](http://blog.revolutionanalytics.com/) then introduces many attempts in the Data Science community to unpack the identity of who that anonymous staffer might be.


###Understanding the problem and steps




###Scraping Tweets

To undertake a project like this it mentions that the task began by scraping the tweets of many White House staffers. How is this done? I am not sure. Let's research that!

Using the all mighty google I found this article: [Scraping Twitter data and using it in R](http://utstat.toronto.edu/~nathan/teaching/sta4002/Class1/scrapingtwitterinR-NT.html)

####1. Install and load appropriate packages

```{r message=FALSE, warning=FALSE}

# INSTALL PACKAGES [only do this once]
# install.packages("twitteR")
# install.packages("tidytext")
# install.packages("dplyr")
# install.packages("ggplot2")

# LOAD PACKAGES
library(twitteR)
library(tidytext)
library(dplyr)
library(ggplot2)
```

####2. Set up Twitter

* You need to have a twitter account 
* Sign up to [https://apps.twitter.com/](https://apps.twitter.com/) with your account
* Once approved click on the "Create an app" link.
* Fill in the details as needed



####3. Fill in Authorisation details

```{r echo=TRUE}

# Replace consumer_key_nt, consumer_secret_nt, access_token_nt and access_secret_nt with your own API keys

# consumer_key <- consumer_key_nt
# consumer_secret <- consumer_secret_nt
# access_token <- access_token_nt
# access_secret <- access_secret_nt

# setup_twitter_oauth(consumer_key, consumer_secret, access_token, access_secret)
```

```{r echo=FALSE}
consumer_key <- 'dIUKlo10XoDeI77t3kZRqmLLp'
consumer_secret <- 'LptQyjZ9vYRept3hboYNFK0IOvqsy1IvEE12VFHAMhOYu9Ex9u'
access_token <- '10455522-QOpzCVAtmX3bsL1PpCxHOk2Vu1X9r1pNQ42RrhZzy'
access_secret <- 'wiBpMYVMUfME6K4VmTqxGNXHn7zGZrh3dKE8zOAwWB0eP'

setup_twitter_oauth(consumer_key, consumer_secret, access_token, access_secret)
```



####4. Using the Twitter Package in R

** What can the TwitteR package do? **

Here are some notes and tutorials on what the TwitteR package for R can do.

[http://geoffjentry.hexdump.org/twitteR.pdf](http://geoffjentry.hexdump.org/twitteR.pdf)

- searchTwitter - search for tweets that match a desired term e.g. hashtags, basic boolean logic such as AND and OR.





**RESEARCH:**
**- what are the limits to how many and capacity of Twitter scraping??**
**- if I did this constantly how do I store/ automate scraping to build a library??**

``` {r echo=FALSE}

fn_twitter <- searchTwitter("#equality",n=1000,lang="en")
fn_twitter_df <- twListToDF(fn_twitter) # Convert to data frame
tweet_words <- fn_twitter_df %>% select(id, text) %>% unnest_tokens(word,text)

tweet_words %>% count(word,sort=T) %>% slice(1:20) %>% 
  ggplot(aes(x = reorder(word, 
    n, function(n) -n), y = n)) + geom_bar(stat = "identity") + theme(axis.text.x = element_text(angle = 60, 
    hjust = 1)) + xlab("")

```


[David Robinson](http://varianceexplained.org/r/op-ed-text-analysis/)
